ms_figures

### 2018-10-15 man/ms_figures.Rmd
add lm for cro_sites

# Lm CA-High
df <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-High')

m1 <- lm(bai_mean ~ year, df)
# summary(m1)
myr2 <- format(summary(m1)$r.squared, digits = 3)

@@

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot. We only show chronologies with # trees > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r myr2`).

@@

# cores 
cronos_bai <- cro_sites %>% filter(n_trees >5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020)) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE) 
  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=6),
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))  
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))

>>>>

# Lm CA-High
dfcaH <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-High')

mCaH <- lm(bai_mean ~ year, dfCaH)
# summary(m1)
r2caH <- format(summary(mCaH)$r.squared, digits = 3)

# Lm CA-Low 
dfCaL <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'CA-Low')

mCaL <- lm(bai_mean ~ year, dfCaL)
r2caL <- format(summary(mCaL)$r.squared, digits = 3)

# Lm SJ
dfSJ <- cro_sites %>% 
  filter(year >= 1975) %>% 
  filter(site == 'SJ')

mSJ <- lm(bai_mean ~ year, dfSJ)
r2SJ <- format(summary(mSJ)$r.squared, digits = 3)

@@

**Figure 4.** Basal Area Increment (BAI) chronologies of *Q. pyrenaica* for northern population (SJ; *green*) and southern ones: low-elevation (CA-Low; *pink*) and high-elevation (CA-High, *purple*) sites. Shading areas coorespond to standard error of the mean. Number of series are displayed in the upper plot. We only show chronologies with # trees > 5. Linear trend since 1975 is shown for southern high-elevation site (CA-High) ($r_2$ = `r r2caH`).

@@

# cores 
cronos_bai <- cro_sites %>% filter(n_trees >5) %>% 
  ggplot(aes(x=year, y=bai_mean/100, colour=site)) + 
  theme_bw() + ylab('BAI') + 
  geom_ribbon(aes(ymin = (bai_mean - bai_se)/100,
                  ymax = (bai_mean + bai_se)/100,
                  fill=site), alpha=.2, colour=NA) +
  geom_line() + 
  geom_point(size=.8) + 
  theme(panel.grid = element_blank(),
        axis.text.x=element_text(size=6),
        legend.position = c(0.1,.8),
        strip.background = element_blank()) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  ylab(expression(paste("BAI (", cm^2, year^-1, ")", sep=''))) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10), limits=c(1815,2020)) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-High'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'CA-Low'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE) +
  geom_smooth(data = subset(cro_sites, year > 1975 & site == 'SJ'), 
              aes(x=year, y=bai_mean/100, colour=site), method = 'lm', se=FALSE)

  # scale_y_continuous(sec.axis = sec_axis(~ ., name = '# trees', breaks = c(0,15,30))) +
  # geom_line(aes(x=year, y=n_trees+40, colour=site)) 
samp <- cro_sites %>% ggplot(aes(x=year, y=n_trees, colour=site)) + 
  theme_bw() + ylab('# trees') + 
  geom_line() + 
  theme(panel.grid = element_blank(),
        legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_text(size=6),
        # axis.text.x=element_blank(),
        # axis.ticks.x=element_blank(), 
        # plot.margin = margin(t = 5, r = 0, b = -5, l = 0, unit = "pt")
        ) + 
  scale_colour_manual(values = colores) +
  scale_fill_manual(values = colores) +
  scale_x_continuous(breaks = seq(1815, 2020, by=10))  
  # theme(plot.margin = unit(c(1,5,-30,6),units="points"),
  #       axis.title.y = element_text(vjust =0.25))
